Notes for General Relativity

### 2016-09-13 Complex Geometry - index/misc/complex geometry-misc.tex
Learns about symmetry in Q.M.
I AM NOT ROBOT.  daily update.

\title{Miscellaneous notes for D. Huybrechts's Complex Geometry}
\date{\today}
\author{Taper}

@@

Then I discover this too hard to work, because too many equations are
involed, and none of them could be eliminiated by other. Meanwhile, I
found a post in Math.SE about this:
\href{http://math.stackexchange.com/questions/923957/set-of-almost-complex-structures-on-mathbb-r4-as-two-disjoint-spheres}{set of almost complex structures on $\mathbb{R}^4$ as two disjoint spheres}.

To understand that post, I read this:
\href{http://math.stackexchange.com/questions/1356823/does-gln-mathbbc-inject-into-gl2n-mathbbr-for-all-n}{Does $GL(n,\mathbb{C})$ inject into $GL^+(2n, \mathbb{R})$ for all $n$?}. However, the proof inside is not perfect:
\begin{quote}
    The claim is: If $V$ is an $n$-dimensional complex vector space with underlying $2n$-dimensional real vector space $W$, then the canonical group monomorphism $\mathrm{GL}(V) \to \mathrm{GL}(W)$ lands inside $\mathrm{GL}^+(W)=\{f \in \mathrm{GL}(W) : \det(f)>0\}$.  The purpose of this abstract reformulation is that we may use operations on vector spaces in order to simplify the problem: If $V'$ is another finite-dimensional complex vector space with underlying real vector space $W'$, the diagram

@@

On the other hand, it seems that this property can be proved directly
by calculation. % TODO Start here and learn that paper.
\begin{thebibliography}{1}
  \bibitem{book} D Huybrechts's Introduction to Complex Geometry. Springer.
\end{thebibliography}
\printnomenclature
\section{License}
The entire content of this work (including the source code
for TeX files and the generated PDF documents) by 
Hongxiang Chen (nicknamed we.taper, or just Taper) is
licensed under a 
\href{http://creativecommons.org/licenses/by-nc-sa/4.0/}{Creative 
Commons Attribution-NonCommercial-ShareAlike 4.0 International 
License}. Permissions beyond the scope of this 
license may be available at \url{mailto:we.taper[at]gmail[dot]com}.
\end{document}

>>>>

% For better indices
\usepackage{tensor}
% ANCHOR
\title{Miscellaneous notes for D. Huybrechts's Complex Geometry}
\date{\today}
\author{Taper}

@@

Then I discover this too hard to work, because too many equations are
involed, and none of them could be eliminiated by other. Meanwhile, I
found a post in Math.SE about this \cite{math.se_1}.

    \subsection{Understand \texorpdfstring{ 
                    $\frac{GL(2n,\mathbb{R})}
                        {GL(n,\mathbb{C})}$
                            }{}
                }
    \label{sec:Understand_GL(2n,R)/GL(n,C)}

    \marginpar{Here I digressed to another problem. I will come back later.}
    To understand that post, I read this\cite{math.se_2}. However, the answer
    in the second post is not perfect:

    \begin{quote}
        The claim is: If $V$ is an $n$-dimensional complex vector space with underlying $2n$-dimensional real vector space $W$, then the canonical group monomorphism $\mathrm{GL}(V) \to \mathrm{GL}(W)$ lands inside $\mathrm{GL}^+(W)=\{f \in \mathrm{GL}(W) : \det(f)>0\}$.  The purpose of this abstract reformulation is that we may use operations on vector spaces in order to simplify the problem: If $V'$ is another finite-dimensional complex vector space with underlying real vector space $W'$, the diagram

@@

    On the other hand, it seems that this property can be proved directly
    by calculation. The following will be a notes of a paper 
    \cite{determinants_of_block_m}, which one comment mentions 
    in the Math.SE post \cite{math.se_2}.

        \subsubsection{Determinants of Block Matrices}
        \label{sec:Determinants of Block Matrices}

        This paper tries to prove the theorem:

        \begin{thm}
            %\label{thm:determinant_of_block_m}
            Let $R$ be a commutative subring of $\tensor[^n]{F}{^n}$,
            where $F$ is a field (or a commutative ring), and let 
            $M\in \tensor[^m]{R}{^m}$. Then 
            \begin{align}
                \text{det}_F \mathbf{M} = 
                    \text{det}_F( \text{det}_R \mathbf{M})
            \end{align}
        \end{thm}

        In particular, we have:
        \begin{align}
            \text{det}_F \left(
                \begin{array}{cc}
                \mathbf{A} & \mathbf{B} \\
                \mathbf{C} & \mathbf{D} \\
                \end{array}
                \right)
                = \text{det}_F (AD-BC)
        \end{align}
        Note that, that the ring being is commutative excludes some
        ambiguity. For example, when the ring $4$ is not commutative,
        then the quantity:

        \begin{align}
            \text{det}_F \left(
                \begin{array}{cc}
                \mathbf{A} & \mathbf{B} \\
                \mathbf{C} & \mathbf{D} \\
                \end{array}
                \right)
        \end{align}
        is not well-defined. It can be $AD-BC$, or $DA-CB$, etc.

        Before the proof of the main theorem, it establishes several
        facts:
        \begin{align}
            \label{eq:sec1.1.1_fact_5}
            \text{det}_F  \left(
                \begin{array}{cc}
                \mathbf{A} & \mathbf{0} \\
                \mathbf{C} & \mathbf{D} \\
                \end{array}
                \right)
                =& \text{det}_F \mathbf{A} \text{det}_F \mathbf{D}
            \\
            \label{eq:sec1.1.1_fact_6}
            \text{det}_F  \left(
                \begin{array}{cc}
                \mathbf{A} & \mathbf{B} \\
                \mathbf{0} & \mathbf{D} \\
                \end{array}
                \right)
                =& \text{det}_F \mathbf{A} \text{det}_F \mathbf{D}
            \\
            \label{eq:sec1.1.1_fact_8}
            \text{det}_F  \left(
                \begin{array}{cc}
                \mathbf{A} & \mathbf{B} \\
                \mathbf{C} & \mathbf{0} \\
                \end{array}
                \right)
                =& \text{det}_F \mathbf{-C} \text{det}_F \mathbf{B}
            \\
            \label{eq:sec1.1.1_fact_88}
            \text{det}_F \mathbf{A} \text{det}_F \mathbf{D}
            =& \text{det}_F \mathbf{I}_n \text{det}_F (\mathbf{AD})
        \end{align}

        He first builds up a seemingly simplified, but is actually
        different version of the main theorem:
        \begin{thm}
            \label{thm:sec_1.1.1_thm3}
            Let $\mathbf{A,B,C,D}\in \tensor[^n]{F}{^n}$. 
            Let $\mathbf{M}=\left(
                \begin{array}{cc}
                \mathbf{A} & \mathbf{B} \\
                \mathbf{C} & \mathbf{D} \\
                \end{array}
                \right)$.

            If
            $\mathbf{CD=DC}$, then,
            \begin{align}
                \text{det}_F \mathbf{M}= 
                \text{det}_F (\mathbf{AD-BC})
            \end{align}
        \end{thm}
        and similar results:
        \begin{align}
            \label{eq:sec1.1.1_thm3_similar}
            \text{if } \mathbf{AC=CA} &\text{then, }
                \text{det}_F \mathbf{M}= \text{det}_F (\mathbf{AD-CB})
            \\
            \text{if } \mathbf{BD=DB} &\text{then, }
                \text{det}_F \mathbf{M}= \text{det}_F (\mathbf{DA-BC})
            \\
            \text{if } \mathbf{AB=BA} &\text{then, }
                \text{det}_F \mathbf{M}= \text{det}_F (\mathbf{DA-CB})
        \end{align}
        These equalities can be proved easily by the following:
        \begin{align*}
            \left(
                \begin{array}{cc}
                 D & 0 \\
                 -C & i \\
                \end{array}
            \right) \left(
                \begin{array}{cc}
                 A & B \\
                 C & D \\
                \end{array}
            \right) &= \left(
                \begin{array}{cc}
                 \text{AD}-\text{BC} & B \\
                 \text{CD}-\text{DC} & D \\
                \end{array}
            \right)=\left(
                \begin{array}{cc}
                 \text{AD}-\text{BC} & B \\
                 0 & D \\
                \end{array}
            \right) \text{ when $C,D$ commutes}
            \\
            \left(
                \begin{array}{cc}
                 D & -B \\
                 0 & i \\
                \end{array}
            \right) \left(
                \begin{array}{cc}
                 A & B \\
                 C & D \\
                \end{array}
            \right) &= \left(
                \begin{array}{cc}
                 \text{DA}-\text{BC} & \text{DB}-\text{BD} \\
                 C & D \\
                \end{array}
            \right)=\left(
                \begin{array}{cc}
                 \text{DA}-\text{BC} & 0 \\
                 C & D \\
                \end{array}
            \right) \text{ when $D,B$ commutes.}
        \end{align*}

        The author also gives an illuminative explanation for why
        $$ \left( \text{det}_F \mathbf{M}- \text{det}_F (\mathbf{AD-BC}) 
            \right) \text{det}_F \mathbf{D} =0 $$
        necessarily implies:
        $$ \text{det}_F \mathbf{M}= \text{det}_F (\mathbf{AD-BC}) $$

% TODO also, this post may be useful:http://math.stackexchange.com/questions/1400917/equivalence-of-almost-complex-structures

\section{Anchor}
\label{sec:Anchor}

\begin{thebibliography}{1}
  \bibitem{book} D Huybrechts's Introduction to Complex Geometry.
  \bibitem{math.se_1} \href{http://math.stackexchange.com/questions/923957/set-of-almost-complex-structures-on-mathbb-r4-as-two-disjoint-spheres}{set of almost complex structures on $\mathbb{R}^4$ as two disjoint spheres}.
  \bibitem{math.se_2} \href{http://math.stackexchange.com/questions/1356823/does-gln-mathbbc-inject-into-gl2n-mathbbr-for-all-n}{Does $GL(n,\mathbb{C})$ inject into $GL^+(2n, \mathbb{R})$ for all $n$?}
  \bibitem{determinants_of_block_m} John R. Silvester, 
      Determinants of Block Matrices. Available in WebArchive link:
      \url{https://web.archive.org/web/20140505161153/http://www.mth.kcl.ac.uk/~jrs/gazette/blocks.pdf}
\end{thebibliography}
\printnomenclature

\section{License}
The entire content of this work (including the source code
for TeX files and the generated PDF documents) by 
Hongxiang Chen (nicknamed we.taper, or just Taper) is
licensed under a 
\href{http://creativecommons.org/licenses/by-nc-sa/4.0/}{Creative 
Commons Attribution-NonCommercial-ShareAlike 4.0 International 
License}. Permissions beyond the scope of this 
license may be available at \url{mailto:we.taper[at]gmail[dot]com}.
\end{document}

### 2016-09-13 G.R/G.R.tex
I AM NOT ROBOT.  daily update.

>>>>

    \subsection{Transformation of velocities}
    \label{sec:Transformation_of_velocities}

    Note that for convenience, I will adopt the popular Lorentz factor
    $\gamma$, defined as:
    \begin{align}
        \gamma \equiv \frac{1}{\sqrt{1-V^2}}
    \end{align}

    To get the similar transofmrations for velocities is quite easy,
    and the result is:
    \begin{align}
        v_x &= \frac{v'_x + V}{1+ v'_x V}\\
        v_y &= \frac{v'_y}{\gamma \left(1+v'x V\right)}\\
        v_z &= \frac{v'_z}{\gamma \left(1+v'x V\right)}\\
    \end{align}

    In the special case when the motion is parallel to the $x$-axis,
    we have (let $v_x$ just be $v$):
    \begin{align}
        v = \frac{v'+V}{1+v' V}
    \end{align}

    Landau mentions that when $V$ is significantly smaller than the
    velocity of light, we have the following approximate formula:
    \begin{align}
        \vec{v} = \vec{v'} + \vec{V} - (\vec{V}\cdot\vec{v'}) \vec{v'}
    \end{align}
